### 2022-03-04 paper/paper.tex
manuscript: proofread and correct paper

% Links
\usepackage{hyperref}
\hypersetup{
	pdftitle={Development of a touch typing trainer with an emphasis on finger-key identification},
	pdfstartview={FitH},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	filecolor=black,
	urlcolor=MidnightBlue
}

@@

%Flowchart
\usepackage{tikz}
\usetikzlibrary{shapes,positioning,calc}

%Tables
\usepackage{booktabs}
\usepackage{supertabular}

@@

@@

	\textsc{Development of a touch typing trainer\\with an emphasis on finger-key identification }
	\par\vspace{0.5cm}

@@

@@

@@

\section{Significance of the Research}
This research is beneficial for all users of physical keyboards. These include a
vast majority of the population as there are a lot of professions that heavily
rely on keyboards. Examples include developers, physicians, educators, and
accountants. By having better ergonomics while typing, wrist injuries can be
prevented, and typing speed may be increased

@@

@@

>>>>

% Links
\usepackage{hyperref}
\hypersetup{
	pdftitle={Development of a finger-key identification submodule for a touch typing trainer},
	pdfstartview={FitH},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	filecolor=black,
	urlcolor=MidnightBlue
}

@@

% Flowchart
\usepackage{tikz}
\usetikzlibrary{shapes,positioning,calc}

% Tables
\usepackage{booktabs}
\usepackage{supertabular}

@@

% Add Gantt Chart
\usepackage{pdfpages}
\usepackage{pdflscape}

@@

	\textsc{Development of a finger-key identification submodule\\for a touch typing trainer}
	\par\vspace{0.5cm}

@@

\section{Research Questions}
\begin{enumerate}
	\item What algorithm or technique using computer vision is capable of
	      identifying which keys are being pressed by which fingers during keyboard
	      typing?
	\item What setup and configuration of a single optical camera can be used to
	      capture images during keyboard typing for real-time finger-key identification
	      using the algorithm identified in 1?
	\item How to design and develop a touch typing trainer using the algorithm in 1
	      and camera setup and configuration in 2?
	\item How accurate is the touch typing trainer in identifying which finger is
	      used to press which key?
	\item What new keyboard typing metric can be developed in order to consider both
	      the key and finger used to press as parameters?
\end{enumerate}

@@

The setup that will be captured will be simplified and fixed for the development
and testing of the finger-key identification submodule. This includes the
keyboard, surface it is placed on, and lighting of the entire area. Furthermore,
the setup will not be tested by other respondents, but by the researchers only
--- as the focus is on the development and testing of the finger-key
identification submodule and not on the touch typing trainer and its effects on
typing.

@@

\section{Significance of the Research}
This research is beneficial for all users of physical keyboards. These include a
vast majority of the population as there are a lot of professions that heavily
rely on keyboards. Examples include developers, physicians, educators, and
accountants. By having better ergonomics while typing --- by touch typing
correctly --- wrist injuries can be prevented, and typing speed may be increased

@@

As such, the expected output of the submodule is the hand and the finger used to
press the key. This allows for a more flexible utilization of the data as it
carries greater context, compared to just returning if the finger used was
correct or not.

@@

\chapter{Gantt Chart}
\begin{landscape}
	\includepdf[pages=-,landscape,scale=0.8,pagecommand={}]{images/gantt-chart.pdf}
\end{landscape}
